AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-02-20 article/tex/main.tex
:fire: initial commit for latex ci build [skip-all]

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

>>>>

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Rocio Montenegro for her input as Montessori teacher. To Elva Corona for her contributions on giving vision to the goals of the project. 
To Marta Perez, Donato Badillo Jr and Antonio Badillo for their interest and initial testers of the project. 
To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
To all of you of whom has limited time and had not able you to contributed as you wished in the project.
Thanks everyone to believe in this project, good things are ahead of us. Miguel Xochicale.
\end{acks}
